---
title: 'Project #2-607'
author: "Robert_M"
date: "October 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```{r}
#Packages to Upload 
library(tidyverse)

#Dataset #1 - Top worldwide movies
#Reading in the data
WW <- url("https://raw.githubusercontent.com/robmercier/Project2/master/TopWWMovies.csv")
TopWWMovies <- read.csv(WW,header = TRUE)

#Changing the names of the columns
names(TopWWMovies)[5] <- "Domestic"
names(TopWWMovies)[6] <- "Domestic%"
names(TopWWMovies)[7] <- "Overseas"
names(TopWWMovies)[8] <- "Overseas%"
head(TopWWMovies)

#Deleting the Caret out of the "Year" column
TopWWMovies$Year. <- gsub("\\^","",TopWWMovies$Year.)
head(TopWWMovies)
summary(TopWWMovies)

#Deleting the extra header band of rows
TopWWMovies <- TopWWMovies[-707,]
TopWWMovies <- filter(TopWWMovies, Rank != "Rank")

View(TopWWMovies)

#Question 1 - Do certain movie studios have a higher average domestic grosses?

#Deleting the Dollar Sign, N/As and the random "k" out of the "Domestic" column
TopWWMovies$Domestic <- gsub("\\$","",TopWWMovies$Domestic)

TopWWMovies$Domestic <- gsub("n/a","",TopWWMovies$Domestic)

TopWWMovies$Domestic <- gsub("k","",TopWWMovies$Domestic)
TopWWMovies$Domestic <- as.numeric(TopWWMovies$Domestic)

#Averaging the totals by studio
TopWWMovies %>%
  group_by(Studio) %>% 
  summarise(average = mean(Domestic))

#Averaging the totals by studio and creating a new data frame
Avg_Studio <- TopWWMovies %>%
  group_by(Studio) %>% 
  summarise(Avg_BO = mean(Domestic)) %>%
  arrange(desc(Avg_BO))
#Answer - Yes there are some studios with higher grosses w/ NM being the highest

#Question 2 - Has international grosses gone up recently?

#Deleting the Dollar Sign out of the "Overseas" column
TopWWMovies$Overseas <- gsub("\\$","",TopWWMovies$Overseas)

TopWWMovies$Overseas<- gsub("n/a","",TopWWMovies$Overseas)

TopWWMovies$Overseas <- as.numeric(TopWWMovies$Overseas)

Intl_Grosses <- TopWWMovies %>%
  group_by(Year.) %>% 
  summarise(Yearly_BO = mean(Overseas)) %>%
  arrange(desc(Yearly_BO))

Intl_Plot <- head(Intl_Grosses, 10)

ggplot(Intl_Plot, aes(Intl_Plot$Year., Intl_Plot$Yearly_BO)) + geom_bar(stat="identity") + geom_text(aes(label=Intl_Plot$Year.), vjust=1.5, color="white") + labs(title = "Yearly Box Office")

#Answer - it is easy to see other than the year 1982, the top move grosses are in the 2000's

#Have movies been getting more popular, grossing more money lately? 
TopWWMovies$Worldwide <- gsub("\\$","",TopWWMovies$Worldwide)

TopWWMovies$Worldwide<- gsub("n/a","",TopWWMovies$Worldwide)

# Code Deletes top movies - 
# TopWWMovies$Worldwide <- as.numeric(TopWWMovies$Worldwide)

Intl_Grosses <- TopWWMovies %>%
  group_by(Year.) %>% 
  summarise(Yearly_BO = mean(Worldwide)) %>%
  arrange(desc(Yearly_BO))
#The codes are not working for this dataframe.


#Dataset #2 - 2018 World cup
#Reading in the data
WC <- url("https://raw.githubusercontent.com/robmercier/hello-world/master/FIFA2018.csv")
FIFA <- read.csv(WC,header = TRUE)

#Deleting the extra header columns
FIFA <- FIFA[-c(23:27)]
FIFA <- FIFA[-c(17:21)]
FIFA <- FIFA[-c(10:14)]

#Checking to see what teams had the most goals in the 2018 World Cup
Goals <- FIFA %>%
  group_by(Team) %>% 
  summarise(Average_Goals = mean(Goal.Scored)) %>% 
  arrange(desc(Average_Goals)) 
#The answer is Belgium 

#Checking to see if Ball Possession is related to goals scored, attempts or passes
cor(FIFA$Ball.Possession.., FIFA$Goal.Scored )
cor(FIFA$Ball.Possession.., FIFA$Attempts)
cor(FIFA$Ball.Possession.., FIFA$Passes)
#Ball Possession is most related to passing, the goals attempted then actual goals
#thinking about it, it makes sense.  Passing it around give the offensive team the 
#ball and moving it back and forth ensures the other team doesn't possess it. 
#since, it is hard to actually score a goal, the possess isn't correlated. 

#The Plot of possession to passes 
plot(FIFA$Ball.Possession.., FIFA$Passes)

#The .88 correlation is quite high.
cor.test(FIFA$Ball.Possession.., FIFA$Passes)

#Dataset #3 - LA Zip COdes
#Reading in the data
LA <- url("https://raw.githubusercontent.com/robmercier/Project2/master/2010_Census_Pop.csv")
Pop <- read.csv(LA,header = TRUE)

Pop %>%
  select(Total.Households) %>% 
  .[[1]] %>%
  min()

#Data cleansing - arranging and making the headers clearer. 
Pop <- Pop %>%
  filter(complete.cases(.)) %>%
  rename('Zip' = Zip.Code, 'Population' = Total.Population, 'Med_Age' = Median.Age, 'Males' = Total.Males, 'females' = Total.Females ,'HHs' = Total.Households, 'HH_Size' = Average.Household.Size) %>%
  arrange((Zip)) %>%
  glimpse()

#sumary of the zip code's populations 
summary(Pop)

#Checking to see what correlations are the highest
cor(Pop)

#graph of population
qqnorm(Pop$Population, pch = 5, frame = FALSE)
qqline(Pop$Population, col = "steelblue", lwd = .5)



```

